\ \break Automatikus korpuszépítés tulajdonnév-felismerés céljára

### 2013-01-03 paper/MSZNY2013/mszny_slides.tex
slide-ok elkezdve

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

@@

\title % (optional, use only with long paper titles)
{Automatically generated NE tagged corpora for English and Hungarian}

@@

\author % (optional, use only with lots of authors)
{Eszter Simon\inst{1}, Dávid Márk Nemeskey\inst{2}}

\institute{\inst{1} Research Institute for Linguistics, Hungarian Academy of Sciences \\
\inst{2} Computer and Automation Research Institute, Hungarian Academy of Sciences} % (optional, but mostly needed)
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date % (optional)
{2012.07.12. \\ ACL NEWS2012 workshop}

@@

\AtBeginSection[]
{
   \begin{frame}
       \frametitle{Outline}
       \tableofcontents[currentsection]
   \end{frame}
}

@@

\section{Introduction}

@@

%\section{Wikipedia and NER}

@@

\section{Creating the English Corpus}

@@

\section{Creating the Hungarian Corpus}

@@

\section{Data Description}

@@

\section{Evaluation}

@@

\section{Conclusions}
\begin{frame}{Conclusions}
  \begin{itemize}
  \vitem We presented freely available NE tagged corpora for English and Hungarian, fully automatically generated from WP
  \vitem We applied a new approach: mapping DBpedia ontology classes to standard CoNLL NE tags, and assigning them to WP entities
  \vitem The huge amount of WP articles opens the possibility of building large enough corpora for less resourced languages such as Hungarian
  \vitem Silver standard corpora can improve NER accuracy in more ways
  \vitem The Hungarian corpus can serve as a training corpus to build NE taggers for non-newswire domains
  \end{itemize}
  \vfill
\end{frame}

@@

{\huge Thank you for your attention!}

@@

emails: \\ {\tt simon.eszter@nytud.mta.hu \\ nemeskey.david@sztaki.mta.hu} \\

@@

the corpora are freely downloadable from {\tt http://hlt.sztaki.hu/resources/}

>>>>

\usepackage[magyar]{babel}
\usepackage[utf8x]{inputenc}

@@

\title % (optional, use only with long paper titles)
{Automatikus korpuszépítés tulajdonnév-felismerés céljára}

@@

\author % (optional, use only with lots of authors)
{Nemeskey Dávid Márk\inst{1}, Simon Eszter\inst{2}}

\institute{\inst{1} MTA SZTAKI \\
\inst{2} MTA Nyelvtudományi Intézet} % (optional, but mostly needed)
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date % (optional)
{2013.01.07. \\ MSZNY 2013}

@@

\AtBeginSection[]
{
   \begin{frame}
       \frametitle{Az előadás vázlata}
       \tableofcontents[currentsection]
   \end{frame}
}

@@

\section{Bevezetés}

@@

\section{Wikipédia és tulajdonnév-felismerés}

@@

\section{Korpuszépítés}

@@

\section{Problémás esetek, hibaelemzés}

@@

\section{A korpuszok leírása}

@@

\section{Kiértékelés}

@@

\section{Összegzés}
\begin{frame}{Conclusions}
  \begin{itemize}
  \vitem We presented freely available NE tagged corpora for English and Hungarian, fully automatically generated from WP
  \vitem We applied a new approach: mapping DBpedia ontology classes to standard CoNLL NE tags, and assigning them to WP entities
  \vitem The huge amount of WP articles opens the possibility of building large enough corpora for less resourced languages such as Hungarian
  \vitem Silver standard corpora can improve NER accuracy in more ways
  \vitem The Hungarian corpus can serve as a training corpus to build NE taggers for non-newswire domains
  \end{itemize}
  \vfill
\end{frame}

@@

{\huge Köszönjük a figyelmet!}

@@

e-mail: \\ {\tt nemeskey.david@sztaki.mta.hu \\ simon.eszter@nytud.mta.hu} \\

@@

URL: \\ {\tt http://hlt.sztaki.hu/resources/}
